Tail associations in ecological variables and their impact on extinction risk

### 2020-03-27 MainText.Rmd
minor edits

---
title: "Tail associations in ecological variables and their impact on extinction risk"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Daniel C. Reuman"
date: ""
fontsize: 12pt
geometry: "left=1in,right=1in,top=1in,bottom=1in"
output: 
  pdf_document:
    number_sections: no
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_maintext.sty

@@

\noindent \emph{Affiliations:}

@@

\noindent Reuman: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66047, USA; Laboratory of Populations, Rockefeller University, 1230 York Ave, New York, NY, 10065, USA

\noindent \emph{Correspondence:} Daniel Reuman, 2101 Constant Ave, Lawrence, KS, 66047, reuman@ku.edu, 626 560 7084.

@@

\noindent The authors were partly supported by US National Science Foundation
grant 1714195 and the James S. McDonnell Foundation.

>>>>

---
title: "Tail associations in ecological variables and their impact on extinction risk"
author:
 - Shyamolina Ghosh\textsuperscript{1}, Lawrence W. Sheppard\textsuperscript{1}, Daniel C. Reuman\textsuperscript{1,2,\dag}
 - \textsuperscript{1}Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA; \textsuperscript{2}Laboratory of Populations, Rockefeller University, 1230 York Ave., New York, NY 10065, USA
date: '\textsuperscript{\dag}Correspondence: Daniel Reuman, 2101 Constant Ave, Lawrence, KS, 66047, reuman@ku.edu, 626 560 7084'
fontsize: 12pt
geometry: "left=1in,right=1in,top=1in,bottom=1in"
output: 
  pdf_document:
    number_sections: no
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_maintext.sty

@@

<!--\noindent \emph{Affiliations:}

@@

\noindent Reuman: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA; Laboratory of Populations, Rockefeller University, 1230 York Ave, New York, NY, 10065, USA

\noindent \emph{Correspondence:} Daniel Reuman, 2101 Constant Ave, Lawrence, KS, 66047, reuman@ku.edu, 626 560 7084. 
-->

@@

\noindent The authors were partly supported by US National Science Foundation
grant 1714195 and the James S. McDonnell Foundation, and the California Department of Fish 
and Wildlife Delta Science Program.
